---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# movies-dataset

<!-- badges: start -->

<!-- badges: end -->

The `movies-dataset` repository contains data scraped from <https://letterboxd.com/>

`download/00-get-users.R` creates the `users.rds` file, which contains user-level information on the 7,500 most popular users of all time.

```{r, message=FALSE, warning=FALSE}
library(vroom)
users <- vroom::vroom("download/users.tsv.gz")
dplyr::glimpse(users)
```

The information contain in the `href` variable was then used to scrape ratings-per user with the `download/01-get-ratings-from-users.R` script. This data is stored in the `user_ratings.rds` file.

```{r}
user_ratings <- vroom::vroom(
  file = "download/user_ratings.tsv.gz", 
  col_types = cols(
    href = col_character(),
    data_film_slug = col_character(),
    data_film_id = col_integer(),
    rating = col_double()
  )
)

dplyr::glimpse(user_ratings)
```

**Number of movies:**

*Note, movies with two raters or less were removed.*

```{r}
length(unique(user_ratings$data_film_slug))
```

**Number of users:**

```{r}
length(unique(user_ratings$href))
```

*Note. When I'm finished scraping, this should be roughly equal to 7500. As of `r format(Sys.Date(), "%B %d %Y")`, the number of users with data represents `r scales::percent(length(unique(user_ratings$href)) / nrow(users), accuracy = 0.01)` of the total users we have sampled.*

**Count of movies rated by users (example):**

```{r movie-raters, message=FALSE, warning=FALSE}
library(tidyverse)
theme_set(theme_light())

user_ratings |> 
  count(data_film_slug) |> 
  ggplot(aes(n)) + 
  geom_histogram(color = "white") + 
  geom_rug(alpha = 1/10) + 
  scale_x_log10() 
```

**A sample of movie ratings (example):**

```{r movie-ratings, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
metadata <- read_rds("download/metadata.rds")

user_ratings |> 
  nest(data = !data_film_slug) |> 
  mutate(n = map_dbl(data, nrow)) |> 
  slice_max(n = 36, order_by = n) |> 
  unnest(cols = "data") |> 
  left_join(select(metadata, data_film_slug, alt), by = "data_film_slug") |> 
  mutate(alt = fct_reorder(alt, -n)) |>
  ggplot(aes(rating)) + 
  geom_bar(width = 1/5) + 
  facet_wrap(~alt, ncol = 4)
```

**Polarizing movies (example):**

```{r polarizing, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
polarizing <- user_ratings |> 
  group_by(data_film_slug) |> 
  filter(n() >= 500) |>
  summarize(var = var(rating)) |> 
  slice_max(n = 36, order_by = var)

user_ratings |> 
  filter(data_film_slug %in% polarizing$data_film_slug) |> 
  left_join(select(metadata, data_film_slug, alt), by = "data_film_slug") |> 
  mutate(alt = fct_reorder(alt, .x = rating, .fun = var, .desc = TRUE)) |>
  ggplot(aes(rating)) + 
  geom_bar(width = 1/5) + 
  facet_wrap(~alt, ncol = 4)
```

**How does the rating of movies of our sample of users compare to the overall ratings?**

*Note. I'm only comparing movies with 10 raters or more.*

```{r comparison, warning=FALSE}
user_ratings |> 
  inner_join(metadata)  |> 
  group_by(data_film_slug, alt) |> 
  filter(n() >= 10) |> 
  summarize(
    all_avg = unique(data_average_rating), 
    sample_avg = mean(rating), 
    sample_size = n()
  ) |> 
  ggplot(aes(all_avg, sample_avg)) + 
  geom_point(aes(color = log(sample_size)), alpha = 1/5) + 
  geom_smooth(method = "lm") + 
  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + 
  ylim(0.5, 5) + xlim(0.5, 5) + 
  theme(legend.position = "bottom") +
  scale_color_viridis_c()
```

Every movie under the red line of equality was rated higher by the full population of users; every movie over the line of equality was rated higher by the sample of popular users. Looks good!

------------------------------------------------------------------------

*We should also add other types of metadata per movie, like date and genre. We can also extract network data (i.e., who among the users follows who), but I wouldn't know how to use that...* 

*Note, there's currently an API in beta. We should consider applying for this so that the data becomes "legal."*

-   <https://letterboxd.com/api-beta/>
-   <https://api-docs.letterboxd.com/>
