---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# movies-dataset

<!-- badges: start -->

<!-- badges: end -->

```{r, message=FALSE}
library(tidyverse)
```

The `movies-dataset` repository contains data scraped from <https://letterboxd.com/>

`download/00-get-users.R` creates the `users.rds` file, which contains user-level information on the 7,500 most popular users of all time.

```{r}
users <- read_rds("download/users.rds")
glimpse(users)
```

The information contain in the `href` variable was then used to scrape ratings-per user with the `download/01-get-ratings-from-users.R` script. This data is stored in the `user_ratings.rds` file.

```{r}
user_ratings <- read_rds("download/user_ratings.rds")
glimpse(user_ratings)
```

Number of movies:

```{r}
length(unique(user_ratings$data_film_slug))
```

Number of users:

```{r}
length(unique(user_ratings$href))
```

*Note. When I'm finished scraping, this should be roughly equal to 7500. As of `r format(Sys.Date(), "%B %d (%Y)")`, the number of users with data represents `r scales::percent(length(unique(user_ratings$href)) / nrow(users), accuracy = 0.01)` of the total users we have sampled.*

Count of movies rated by users (example):

```{r movie-raters}
user_ratings |> 
  count(data_film_slug) |> 
  ggplot(aes(n)) + 
  geom_histogram(color = "white") + 
  geom_rug(alpha = 1/10) + 
  scale_x_log10() 
```

A sample of movie ratings (example):

```{r movie-ratings,  message=FALSE, warning=FALSE, fig.height=8}
metadata <- read_rds("download/metadata.rds")

user_ratings |> 
  filter(!is.na(rating)) |> 
  nest(data = !data_film_slug) |> 
  mutate(n = map_dbl(data, nrow)) |> 
  slice_max(n = 24, order_by = n) |> 
  unnest(cols = "data") |> 
  left_join(select(metadata, data_film_slug, alt), by = "data_film_slug") |> 
  mutate(alt = fct_reorder(alt, -n)) |>
  ggplot(aes(rating)) + 
  geom_bar(width = 1/5) + 
  facet_wrap(~alt, ncol = 3)
```

**How does the rating of movies of our sample of users compare to the overall ratings?**

```{r comparison, warning=FALSE}
inner_join(metadata, user_ratings) |> 
  filter(!is.na(rating)) |> 
  group_by(data_film_slug, alt) |> 
  summarize(all_avg = mean(data_average_rating), sample_avg = mean(rating), sample_size = n()) |> 
  ggplot(aes(all_avg, sample_avg)) + 
  geom_jitter(aes(color = log(sample_size)), alpha = 1/10) + 
  geom_smooth(method = "lm") + 
  geom_abline(slope = 1, intercept = 0, color = "red", linetype = "dashed") + 
  ylim(0.5, 5) + xlim(0.5, 5) + 
  theme(legend.position = "bottom") + 
  scale_color_viridis_c()
```

This graph makes it look like our more popular users are different from *all* users. Every movie under the red line of equality was rated higher by the full population of users; every movie over the line of equality was rated higher by the sample of popular users. But, as the colors show, this is simply an issue of sample size; all high-sample movies cluster near the line of equality. This means we might not have "biased" samples after all.

------------------------------------------------------------------------

*We should also add other types of metadata per movie, like date and genre. We can also extract network data (i.e., who among the users follows who), but I wouldn't know how to use that...* 

*Note, there's currently an API in beta. We should consider applying for this so that the data becomes "legal."*

-   <https://letterboxd.com/api-beta/>
-   <https://api-docs.letterboxd.com/>
